Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2017-12-19 ms.tex
andrew

@@

The retrieved C/O is consistent with solar, with a $1\sigma$ confidence interval of $0.54 - 0.85$. We infer an upper limit on C/O of 0.9 at $3\,\sigma$ confidence, driven by the fact that the atmospheric chemistry is expected to change dramatically when C/O exceeds unity. For a carbon-rich composition, the equilibrium abundance of methane relative to CO increases by orders of magnitude compared to an oxygen-rich  composition \citep[e.g.][]{madhusudhan11}. The \Spitzer\ eclipse depths are sensitive to the relative abundance of these species, so we can confidently rule out a carbon-rich composition in spite of the lack of spectrally resolved features.  
Thermal structure.

We note that an important caveat for our results is that the best fit model is not a perfect fit to the data (with $\chi_\nu = 1.77$), so the uncertainties produced by the MCMC may be underestimated. Furthermore, the inferred C/O and metallicity are highly sensitive to the large planet-to-star flux at \Spitzer $4.5\mu$m, which is the worst fit data point. (With this point removed, the fit quality is significantly improved: $\chi_\nu = 1.17$).  The dominant absorbing species over the $4.5\,\mu$m bandpass is CO, so to fit this point the model tends to favor super-solar metallicities and C/O. Given that the result is driven by a single photometric band and there are no resolved molecular features to constrain the absorbers that are present or the temperature-pressure profile, we caution against over-interpreting these results until wider spectral coverage is available.

>>>>

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/WASP-103b_grid_DAYSIDE_stair_pairs_02.pdf}
\caption{Posterior distributions for WASP-103b's atmospheric heat redistribution, metallicity, and C/O, from a retrieval of the dayside emission spectrum. The histograms on the diagonal show the marginalized distribution of each parameter, with dashed lines indicating the median and surrounding 68\% confidence interval. The colored shading on the off-diagonal panels indicates FIXME. The blue lines correspond to solar metallicity (1) and C/O (0.54).}
\label{fig:composition}
\end{figure}

@@

The retrieved C/O is consistent with solar, with a $1\sigma$ confidence interval of $0.54 - 0.85$. We infer an upper limit on C/O of 0.9 at $3\,\sigma$ confidence, driven by the fact that the atmospheric chemistry is expected to change dramatically when C/O exceeds unity. For a carbon-rich composition, the equilibrium abundance of methane relative to CO increases by orders of magnitude compared to an oxygen-rich  composition \citep[e.g.][]{madhusudhan11}. The \Spitzer\ eclipse depths are sensitive to the relative abundance of these species, so we can confidently rule out a carbon-rich composition in spite of the lack of spectrally resolved features.

Thermal structure.

We note that an important caveat for our results is that the best fit model is not a perfect fit to the data (with $\chi_\nu = 1.77$), so the uncertainties produced by the MCMC may be underestimated. Furthermore, the inferred C/O and metallicity are highly sensitive to the planet-to-star flux at \Spitzer $4.5\mu$m, which is the worst fit data point. (With this point removed, the fit quality is significantly improved: $\chi_\nu = 1.17$).  The dominant absorbing species over the $4.5\,\mu$m bandpass is CO, so to fit this point the model tends to favor super-solar metallicities and C/O. Given that the result is driven by a single photometric band and there are no resolved molecular features to constrain the temperature-pressure profile or which absorbers are present, we caution against over-interpreting these results until wider spectral coverage is available.
